---
title: "Assignment 2"
format: html
editor: visual
---

## Assignment 2

This is all the code I used to complete Assignment 2.

## Loading Packages and Data

Loading in the data and removing all data for participants with N/A for answers

```{r}
#| label: Load packages and data

install.packages("remotes")

remotes::install_github("dustinfife/flexplot")

install.packages("apaTables")

library(haven)
library(tidyverse)
library(dplyr)
library(flexplot)
library(apaTables)

## Loading in the data
PSYR6003_A2 <- read_sav("PSYR6003.A2.sav")

A2 <- na.omit(PSYR6003_A2)
View(A2)

```

Making sex a factor rather than just a numerical variable
```{r}
#| label: Making Sex a Factor 

A2 <- A2 %>% 
  mutate(sex = as.factor(sex)) %>% 
  mutate(sex = ifelse(sex == "Female", 0, 1))

#Checking to ensure the previous code worked
view(A2)

```

## Reverse Coding and Calculating Subscale Means

Reverse coding tipm.CONS2.3y and then using this new score to calculate the 

```{r}
#| label: Reverse Code and Subscale Means

## I first need to reverse code question tipm.CONS2.3y

A2 <- A2 %>%
  mutate(reverse_CONS2 = 8 - tipm.CONS2.3y)
view(A2$reverse_CONS2)  

# Now that I have reverse-coded the tipm.CONS2.3y question I can calculate the mean score totals for SPP, negative affect, and conscientiousness 

#SPP
A2 <-  mutate(A2, SPP_summed = (mps.SPP1.3y + mps.SPP2.3y + mps.SPP3.3y + mps.SPP4.3y + mps.SPP5.3y)/5)

#Negative affect

A2 <-  mutate(A2, NegAff_summed = (guilt1.3y + guilt2.3y + guilt3.3y + dep1.3y + dep2.3y + dep3.3y + fear1.3y + fear2.3y + fear3.3y + host1.3y + host2.3y + host3.3y)/12)

#Conscientiousness
A2 <-  mutate(A2, CONS_summed = (tipm.CONS1.3y+reverse_CONS2)/2)

```

## H1

Sex and conscientiousness is associated with negative affect. Women > NA, conscientiousness neg. corr. to NA. SPP pos. corr. w/ NA. Sex, conscientiousness 
and SPP covary (hard to detect unique effects). Show incremental validity of SPP
to predict NA more than sex and conscientiousness. 

H1: Sex, conscientiousness and SPP predict NA. MR will be used w/ the GLM 

```{r}
#| label: H1 Calculations

# Step 1: Creating the regression model with the summed NA 

H1 <- lm(NegAff_summed~sex+CONS_summed+SPP_summed, data = A2)

#Step 2: Visualize the plots

visualize(H1)

#Step 3: Model Output

estimates(H1)

```

Explanation of graphs to help with write up: 
--  HoR is approximately normally distributed but shows a slight right skew. If this      is the only violation of the assumptions, the model is still considered reliable.     However, if other assumptions are also violated, the model may not be valid.

--  RDP is relatively flat with a slight curve at the lower and upper ends but does       not seem to be enough for us to consider using a quadratic.** Asked Ashley
    ** you’re good to just mention it appears to be violated and that a quadratic or        other model may be a better fit and move along as if the assumption was met!

--  S-L plot shows that the line of variance is relatively flat and straight meaning      the homoskedasticity assumption has been met.

--  Assumption of Independence is met because the participants most likely did not        influence each others scores since we can assume they did not interact while          completing the survey. Especially in undergraduate survey research, most of it is     online meaning people can complete it at their own convenience and not have to be     in a testing facility where they can discuss with other participants. 

```{r}

#Step 4: Creating an APA table with the all the regression data. It will be Table 1 and provides the predictor, regression coefficient (b), regression coefficient with 95% CI [Upper and Lower Limit], beta (standardized regression coefficient), beta with 95% CI [Upper and Lower Limit], squared partial correlations (sr^2), squared partial correlation 95% CI [Upper and Lower Limit], correlation coefficient (r), and Fit which is how well the model fits the data

apa.reg.table(H1, filename = "H1 Regression Table 1.doc", table.number = 1)

```


Table 1 Analysis: Sex predicts NA and being female predicts having more negative affect (b = -0.56 [-0.97, -0.15]). Conscientiousness negatively predicts NA (b = -0.26 [-0.38, -0.15]). SPP predicts NA (b = 0.20 [0.10, 0.30]). The whole model predicts negative affect (R2 = 0.269 [.13, 0.37]); hypothesis #1 is confirmed. Table 1 provides all the details of the regression mentioned above. 

```{r}

#| label: Bivariate Correlations for H1

apa.reg.table(H1, filename= "H1 Regression Table 2. doc", table.number = 2, prop.var.conf.level = 0.95)

```

Table 2 Analysis : Bivariate correlations between sex, conscientiousness, and SPP. The correlation between NA and CONS and SPP are significant. The correlation between NA and sex was not significant. The correlations between NA and sex and CONS are negative and the correlation between NA and SPP is positive. Since both CONS and SPP have similar r (despite one being negative) meaning their effects may overlap. Since CONS and SPP are both significantly correlated we must test if SPP explains some of the variance in NA when controlling for sex and conscientiousness. This will test whether SPP adds meaningful, incremental value to the prediction of NA. This is H2.  

## H2

Sex and conscientiousness is associated with negative affect. Women > NA, conscientiousness neg. corr. to NA. SPP pos. corr. w/ NA. Sex, conscientiousness 
and SPP covary (hard to detect unique effects). Show incremental validity of SPP
to predict NA more than sex and conscientiousness.

H2: SPP will predict unique variance in NA when controlling sex and conscientiousness

```{r}
#| label: H2 Calculations

## Correlations for all the variables

H2 <- select(A2, NegAff_summed, CONS_summed, SPP_summed, sex)

apa.cor.table(H2, table.number = 3, filename = "H2 Correlation Table 3.doc")
  
```

```{r}
#| label: Table 4 code

## Using this code to examine the regression coefficients and other data from the regression for the Control model (with only CONS and sex) and the Predictor model (CONS, SPP, and sex). The Control model is essentially the reduced model and the Predictor model is essentially the full model. 

Reduced <- lm(NegAff_summed ~ CONS_summed + sex, data = A2)
Full <- lm(NegAff_summed ~ CONS_summed + SPP_summed + sex, data = A2)

Table4 <- apa.reg.table(Reduced, Full,
                        table.number = 4,
                        filename="H2 Regression Control and Predictor Table 4.doc")
```

Step 1: 
-- Research question: How does SPP predict NA after controlling for sex and conscientiousness?

Step 2:
-- GLM Format

NA = b0 + b1(sex) + b2(CONS) + b3(SPP) + e

Step 3:
-- Parameter of interest

NA = b0 + b1(sex) + b2(CONS) + b3(SPP) + e

Step 4:
-- Creating a reduced and full model

Reduced -- NA = b0 + b1(sex) + b2(CONS) + e
Full -- NA = b0 + b1(sex) + b2(CONS) + b3(SPP) + e

```{r}
#| label: Comparing Reduced and Full Model

# Creating a reduced and full model. Reduced does not include SPP but the full model contains SPP.

# The "Reduced" and "Full" objects were created for Table 4 so there is no need to make them again here but I will call on them from the previous block of code. 

model.comparison(Reduced, Full)

```

Full model has a lower AIC and BIC compared to the reduced model and the Bayes factor is much higher which indicates that the full model fits the data better than the reduced model. Conclusion: H2 is confirmed meaning that SPP predicts unique variance in negative affect over and above sex and conscientiousness. 




