---
title: "Assignment 2"
format: html
editor: visual
---

## Assignment 2

This is all the code I used to complete Assignment 2.

## Loading Packages and Data

Loading in the data and removing all data for participants with N/A for answers

```{r}
#| label: Load packages and data

install.packages("remotes")

remotes::install_github("dustinfife/flexplot")

install.packages("apaTables")

library(haven)
library(tidyverse)
library(dplyr)
library(flexplot)
library(apaTables)

## Loading in the data
PSYR6003_A2 <- read_sav("PSYR6003.A2.sav")

A2 <- na.omit(PSYR6003_A2)
View(A2)

```

Making sex a factor rather than just a numerical variable
```{r}
#| label: Making Sex a Factor 

A2 <- A2 %>% 
  mutate(sex = as.factor(sex)) %>% 
  mutate(sex = ifelse(sex == "Female", 0, 1))

#Checking to ensure the previous code worked
view(A2)

```

## Reverse Coding and Calculating Subscale Means

Reverse coding tipm.CONS2.3y and then using this new score to calculate the 

```{r}
#| label: Reverse Code and Subscale Means

## I first need to reverse code question tipm.CONS2.3y

A2 <- A2 %>%
  mutate(reverse_CONS2 = 8 - tipm.CONS2.3y)
view(A2$reverse_CONS2)  

# Now that I have reverse-coded the tipm.CONS2.3y question I can calculate the mean score totals for SPP, negative affect, and conscientiousness 

#SPP
A2 <-  mutate(A2, SPP_summed = (mps.SPP1.3y + mps.SPP2.3y + mps.SPP3.3y + mps.SPP4.3y + mps.SPP5.3y)/5)

#Negative affect

A2 <-  mutate(A2, NegAff_summed = (guilt1.3y + guilt2.3y + guilt3.3y + dep1.3y + dep2.3y + dep3.3y + fear1.3y + fear2.3y + fear3.3y + host1.3y + host2.3y + host3.3y)/12)

#Conscientiousness
A2 <-  mutate(A2, CONS_summed = (tipm.CONS1.3y+reverse_CONS2)/2)

```

## Hypotheses to Test

Sex and conscientiousness is associated with negative affect. Women > NA, conscientiousness neg. corr. to NA. SPP pos. corr. w/ NA. Sex, conscientiousness 
and SPP covary (hard to detect unique effects). Show incremental validity of SPP
to predict NA more than sex and conscientiousness. 

H1: Sex, conscientiousness and SPP predict NA. MR will be used w/ the GLM 

```{r}

# Step 1: Creating the regression model with the summed NA 

H1 <- lm(NegAff_summed~sex+CONS_summed+SPP_summed, data = A2)

#Step 2: Visualize the plots

visualize(H1)

#Step 3: Model Output

estimates(H1)

#Step 4: Creating an APA table with the all the  

apa.reg.table(H1, filename = "H1.doc", table.number = 1)

```

Explanation of graphs to help with write up: 
--  HoR is approximately normally distributed but shows a slight right skew. If this      is the only violation of the assumptions, the model is still considered reliable.     However, if other assumptions are also violated, the model may not be valid.

--  RDP is relatively flat with a slight curve at the lower and upper ends but does       not seem to be enough for us to consider using a quadratic.** Asked Ashley

--  S-L plot shows that the line of variance is relatively flat and straight meaning      the homoskedasticity assumption has been met.

--  Assumption of Independence is met because the participants most likely did not        influence each others scores since we can assume they did not interact while          completing the survey. Especially in undergraduate survey research, most of it is     online meaning people can complete it at their own convenience and not have to be     in a testing facility where they can discuss with other participants. 



## H2: SPP will predict unique variance in negative affect over and above sex and conscientiousness in a meaningful way.
